---
output:
  bookdown::github_document2:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  tidy = "styler"
)
```

# jladown
test
<!-- badges: start -->
<!-- badges: end -->

The goal of jladown is to provide a reproducible template for the Journal of Learning Analytics using R Markdown in multiple formats such as pdf, gitbook, and Word.

## Installation

`jladown` is currently under development on GitHub. Please install and test the package as follows:

```{r installation, eval = FALSE}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github('jooyoungseo/jladown')
```

## Example

This is a basic example which shows you how to use `jladown` package. While 
other formats are usable, `pdf` output is fully supported at this moment.

### Loading package

```{r}
library(jladown)
```

## For non-RStudio users

For non-RStudio users, you may create a project template in the current path 
with the following function:

```{r}
jladown:::jladown_skeleton('.')
```

## For RStudio users

For RStudio users, as long as `jladown` is installed, you can create a project 
by creating a new R Markdown Document. From within RStudio, select "File" -> 
"New File" -> "R Markdown", and then select the *Journal of Learning Analytics* 
(`jladown) template.
 

# To-Do List

- [x] Add auto-word-counting capability using `rmdfiltr` package internally.
- [ ] Fix `template.docx` does not take any effect on `jladown::jla_word()` output.
- [ ] Make a cover page including jla logo for `bookdown::gitbook()` output.
