---
output:
  bookdown::github_document2:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  tidy = "styler"
)
```
test
# jladown

<!-- badges: start -->
<!-- badges: end -->

The goal of jladown is to provide a reproducible template for the Journal of Learning Analytics using R Markdown in multiple formats such as pdf, gitbook, and Word.

## Installation

`jladown` is currently under development on GitHub. Please install and test the package as follows:

```{r installation, eval = FALSE}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github('jooyoungseo/jladown')
```

## Example

This is a basic example which shows you how to use `jladown` package.

While other formats are usable, `pdf` output is fully supported at this moment.

``` r
## Loading package:
library(jladown)

## Create a project template in current path (for non-RStudio users):
jladown:::jladown_skeleton('.')
## RStudio users: please use "New Project" and `jladown` template there.

## After editing, use the bookdown knit button in RStudio; if you don't use RStudio, do the following in your R console:
bookdown::render_book("my_article.Rmd", output_format = "all")
```

# To-Do List

- [x] Add auto-word-counting capability using `rmdfiltr` package internally.
- [ ] Fix `template.docx` does not take any effect on `jladown::jla_word()` output.
- [ ] Make a cover page including jla logo for `bookdown::gitbook()` output.
